Julia for HPC: In Situ Data Analysis with Julia for Climate Simulations at Large Scale

### 2024-06-18 paper/paper.tex
Update paper.tex

The in situ approach has been studied in recent years and has been employed in different aspects of HPC. First, there are existing in situ frameworks, such as Ascent~\cite{ascent}, ParaView Catalyst~\cite{catalyst}, SENSEI~\cite{sensei_url}, VisIt libSIM~\cite{visit}, and SmartSim~\cite{chen2016smartsim}. These developed frameworks aim to help users build data analysis and data visualization, but none of them supports the Julia programming language. Second, the open-sourced ADIOS/ADIOS2~\cite{adios, godoy2020adios} data I/O system and the studies of Chimbuko/CODAR~\cite{kelly2020chimbuko} have explored data reduction for in situ approaches and researched the performance optimization of the whole in situ data analysis workflow. Last, previous studies have been made on optimizing the complex workflow that involves complex HPC applications and post-hoc data analysis. However, these studies still require significant I/O on disk storage and are not able to help reduce the data. For a more comprehensive summary of in situ infrastructures, readers are referred to~\cite{insitu_star,insitu_terminology}.

@@

The Julia interface mainly defines the format of input data, so all in situ Julia data analysis methods can be plugged-in without additional E3SM compilation, thanks to Julia's Just-in-time (JIT) compilation.
As discussed previously, another key design of the Julia interface is to correctly convert the Fortran MPI communicator to Julia MPI communicator, which enables the algorithm developers to write their analysis routines using the same EAM MPI communicator. Due to the low-level MPI implementations, different MPI libraries (i.e., OpenMPI, MPICH, and MVAPICH) require specific converters; the following code snippet shows the converter implementations~\cite{gabriel2004open,panda2021mvapich,gropp1996user}.

>>>>

The in situ approach has been studied in recent years and has been employed in different aspects of HPC. First, there are existing in situ frameworks, such as Ascent~\cite{ascent}, ParaView Catalyst~\cite{catalyst}, SENSEI~\cite{bethel2022sensei}, VisIt libSIM~\cite{visit}, and SmartSim~\cite{chen2016smartsim}. These developed frameworks aim to help users build data analysis and data visualization, but none of them supports the Julia programming language. Second, the open-sourced ADIOS/ADIOS2~\cite{adios, godoy2020adios} data I/O system and the studies of Chimbuko/CODAR~\cite{kelly2020chimbuko} have explored data reduction for in situ approaches and researched the performance optimization of the whole in situ data analysis workflow. Last, previous studies have been made on optimizing the complex workflow that involves complex HPC applications and post-hoc data analysis. However, these studies still require significant I/O on disk storage and are not able to help reduce the data. For a more comprehensive summary of in situ infrastructures, readers are referred to~\cite{insitu_star,insitu_terminology}.

@@

The Julia interface mainly defines the format of input data, so all in situ Julia data analysis methods can be plugged-in without additional E3SM compilation, thanks to Julia's Just-in-time (JIT) compilation.
As discussed previously, another key design of the Julia interface is to correctly convert the Fortran MPI communicator to Julia MPI communicator, which enables the algorithm developers to write their analysis routines using the same EAM MPI communicator. Due to the low-level MPI implementations, different MPI libraries (i.e., OpenMPI, MPICH, and MVAPICH) require specific converters; the following code snippet shows the converter implementations~\cite{gabriel2004open,panda2021mvapich,gropp1996high}.
